Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-05-08 index.qmd
adding STOTEN submission

@@

>>>>

---dd .

@@

```{r Figure1 Map Graphical abstract}
#| cache: true
#| echo: false
#| eval: false
#| warning: false

  df_P2<-Projects_df %>% 
    mutate(ID = c(1:nrow(.))) %>% 
    mutate(Site = case_when(ID == 1 ~ "Aveiro Lagoon",
                            ID == 2 ~ "Morbihan Gulf",
                            ID == 3 ~ "Bourgneuf Bay",
                            TRUE ~ "NA"),
           ID = case_when(ID == 1 ~ "Portugal",
                          ID == 2 ~ "France",
                          TRUE ~ "France")) %>% 
    dplyr::select(c(lon,lat,ID,Site))

p2  <-
  ggplot(MiniEU_map) +
  geom_sf(linewidth=0.5,alpha=0.93,
          fill="#CFCFCF",colour="grey30")+
    ggforce::geom_mark_ellipse(data=df_P2,
                 aes(x=lon,
                     y=lat,
                     label = ID,
                     description=Site) ,
                 linewidth=0.3,
                 label.width = 20,
                 fill="goldenrod",
                 show.legend=F,
                 label.hjust = 0.5,
                 con.size = 2,
                 con.colour = "goldenrod4",
                 label.fontsize = c(25,20),
                 alpha=0.8,
                 expand = unit(2, "mm") , 
                 radius = unit(2, "mm") , 
                 label.buffer = unit(10, "mm") ,
                 label.fill = "grey90")+
  coord_sf(xlim=c(2600000,4100000) ,
          ylim=c(1600000,3100000))+
  theme_void()+
  labs(x="Longitude",
       y="Latitude")+
  scale_y_continuous(labels=scaleFUN)
  # theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm"),
  #       axis.title = element_blank(),
  #       axis.text.x = element_text(size = 20),
  #       axis.text.y = element_text(size = 20) )

ggsave("Figures/High_res/Figure1/Graphical_Abstract_Map.png",p2,width= 10, height=10)
